Gravitational-wave sensitivity curves

### 2014-07-02 Sources.tex
small changes to section 5

\section{Astrophysical sources}\label{sec:sources}
All the sources described here are represented by boxes in figures \ref{fig:hc}, \ref{fig:S} and \ref{fig:omega}. The boxes are drawn in such a way that there is a reasonable event rate for sources at a detectable SNR. Descriptions of each source are given in the following sections. Sources with short durations (i.e., burst sources) and sources which evolve in time over much longer timescales than our observations are drawn with flat topped boxes. Inspiralling sources which change their frequency over observable timescales are drawn with sloping tops. The slope for the top of the box is chosen to be $-2/3$ for all sources, which is also the appropriate gradient for a stochastic backgrounds of binaries. The width of the box gives the range of frequencies sources of a given type can have a while remaining at a detectable amplitude.

@@

\subsubsection{Galactic white dwarf binaries} \label{sec:GB}

\cjm{This section should probably be larger and more detailed. These are by far the most numerous sources and at the moment I don't even mention verification binaries.}

These divide into two classes, the unresolvable and the resolvable galactic binaries. The distinction between resolvable and unresolvable is detector specific; here we choose LISA. For the unresolvable binaries the box plotted corresponds to the estimate of the background due to \cite{Nelemans},
\begin{equation} h_{c}(f)= 5\times 10^{-21} \left(\frac{f}{10^{-3}\,\textrm{Hz}}\right)^{-2/3} \; . \end{equation}
This background is unchanging over the mission lifetime, therefore, as discussed in section \ref{sec:PTAgeneralproperties}, when plotting the amplitude on a sensitivity curve plot an observation time must be specified; here an observation time of one year is used. Estimates for the event rate of resolvable binaries centre around ${\cal{O}}(10^{3})$ events for eLISA. The box plotted in figures \ref{fig:hc}, \ref{fig:S} and \ref{fig:omega} has an ratio $h_{c}/h_{n}=50$ for eLISA at its peak sensitivity, the frequency range of the box is $\left(3\times10^{-4}\right.$--$\left.10^{-2}\right)~\mathrm{Hz}$, based on visual inspection of Monte Carlo population simulation results presented in \cite{Amaro-Seoane-et-al}.

>>>>

\section{Astrophysical sources}\label{sec:sources}
All the sources described here are represented by shaded boxes in figures \ref{fig:hc}, \ref{fig:S} and \ref{fig:omega}. The boxes are drawn in such a way that there is a reasonable event rate for sources at a detectable SNR. Descriptions of each source are given in the following sections. Sources with short durations and sources which evolve in time over much longer timescales than our observations are drawn with flat topped boxes. Inspiralling binaries, or stochastic backgrounds of binaries, are drawn with a sloping top proportional to $f^{-2/3}$, which is result derived in section \ref{sec:stoch}. The width of the box gives the range of frequencies sources of a given type can have a while remaining at a detectable amplitude.

@@

\subsubsection{Galactic white dwarf binaries} \label{sec:GB}
These are the most numerous GW sources, they are also the only source where several guaranteed sources have already been indentified by electromagnetic observations, these are known as the verification binaries, \cite{2006CQGra..23S.809S}.

Galactic binaries divide into two classes; the unresolvable and the resolvable galactic binaries. The unresolvable binaries overlap to form a stochastic background as discussed in section \ref{sec:stoch}. Plotted in figures \ref{fig:hc}, \ref{fig:S} and \ref{fig:omega} is the estimate of this background 
due to \cite{Nelemans} where an observation time of one year has been assumed
\begin{equation} h_{c}(f)= 5\times 10^{-21} \left(\frac{f}{10^{-3}\,\textrm{Hz}}\right)^{-2/3} \; . \end{equation}
Estimates for the event rate of resolvable binaries centre around ${\cal{O}}(10^{3})$ events for eLISA. The box plotted in figures \ref{fig:hc}, \ref{fig:S} and \ref{fig:omega} has an ratio $h_{c}/h_{n}=50$ for eLISA at its peak sensitivity, the frequency range of the box is $\left(3\times10^{-4}\right.$--$\left.10^{-2}\right)~\mathrm{Hz}$, based on visual inspection of Monte Carlo population simulation results presented in \cite{Amaro-Seoane-et-al}.
